Taking Dyads Seriously

### 2018-08-01 paper/netsMatter.tex
add word count to title
non anon version for apsa

% \title{Taking Dependencies Seriously:\\A Latent Network Approach to Dyadic Analysis}
% \title{Taking Dyads Seriously:\\A Latent Network Approach to Dyadic Analysis}
\title{Taking Dyads Seriously}
\vspace{\baselineskip}

% \author[Minhas]{Shahryar Minhas}
% \address{Shahryar Minhas: Department of Political Science}
% \curraddr{Michigan State University}
% \email[Corresponding author]{minhassh@msu.edu}

% \author[Dorff]{Cassy L. Dorff}
% \address{Cassy L. Dorff}
% \curraddr{Department of Political Science, University of New Mexico}
% \email{cdorff@unm.edu}

% \author[Foster]{Margaret Foster}
% \address{Margaret Foster}
% \curraddr{Department of Political Science, Duke University}
% \email{margaret.foster@duke.edu}

% \author[Gallop]{Max Gallop}
% \address{Max Gallop}
% \curraddr{Department of Government and Public Policy, University of Strathclyde}
% \email{max.gallop@strath.ac.uk}

% \author[Liu]{Howard Liu}
% \address{Howard Liu}
% \curraddr{Department of Political Science, Duke University}
% \email{hao.liu@duke.edu}

% \author[Tellez]{Juan Tellez}
% \address{Juan Tellez}
% \curraddr{Department of Political Science, Duke University}
% \email{juan.tellez@duke.edu}

% \author[Ward]{Michael D. Ward}
% \address{Michael D. Ward}
% \curraddr{Department of Political Science, Duke University}
% \email{michael.d.ward@duke.edu}

% % \date{\today}

%\thanks{Shahryar Minhas and Michael D. Ward acknowledge support from National Science Foundation (NSF) Award 1259266. John Ahlquist, Robert Franzese, and Arturas Rozenas provided welcome and helpful comments. We also thank Douglas Gibler for kindly providing us with a copy of the data and programs he used in \citet{gibler:2017}. We benefited from presentations of this material at the 2017 Political Methodology Conference, and our home institutions.}

@@

\maketitle\thispagestyle{empty}
\newpage\setcounter{page}{1}

>>>>

\title{Taking Dyads Seriously}
\vspace{\baselineskip}

\author[Minhas]{Shahryar Minhas}
\address{Shahryar Minhas: Department of Political Science}
\curraddr{Michigan State University}
\email[Corresponding author]{minhassh@msu.edu}

\author[Dorff]{Cassy L. Dorff}
\address{Cassy L. Dorff}
\curraddr{Department of Political Science, University of New Mexico}
\email{cdorff@unm.edu}

\author[Foster]{Margaret Foster}
\address{Margaret Foster}
\curraddr{Department of Political Science, Duke University}
\email{margaret.foster@duke.edu}

\author[Gallop]{Max Gallop}
\address{Max Gallop}
\curraddr{Department of Government and Public Policy, University of Strathclyde}
\email{max.gallop@strath.ac.uk}

\author[Liu]{Howard Liu}
\address{Howard Liu}
\curraddr{Department of Political Science, Duke University}
\email{hao.liu@duke.edu}

\author[Tellez]{Juan Tellez}
\address{Juan Tellez}
\curraddr{Department of Political Science, Duke University}
\email{juan.tellez@duke.edu}

\author[Ward]{Michael D. Ward}
\address{Michael D. Ward}
\curraddr{Department of Political Science, Duke University}
\email{michael.d.ward@duke.edu}

% \date{\today}

\thanks{Shahryar Minhas and Michael D. Ward acknowledge support from National Science Foundation (NSF) Award 1259266. Peter Hoff, John Ahlquist, Robert Franzese, Arturas Rozenas, and Benjamin Appel provided welcome and helpful comments. We also thank Douglas Gibler for kindly providing us with a copy of the data and programs he used in \citet{gibler:2017}. We benefited from presentations of this material at the 2017 Political Methodology Conference, and our home institutions.}

@@

\maketitle

\begin{center}
	\textbf{Word count}: 9,177
\end{center}

\thispagestyle{empty}
\newpage\setcounter{page}{1}
